\vskip-0.6in \Large Political Uncertainty

### 2015-03-23 GS-extension.tex
work out FOC for vote buyer B in terms of PDF

					\item 

@@

	\item Vote buyer A
			\item Whatever we decide for vote buyer B will be the same for vote buyer A
\end{enumerate}

>>>>

					\item It's easier for me to think of the CDF in terms of the non-standardized Normal distribution before taking the derivative. Then, if my math is right, the FOC becomes
							  \frac{1}{\beta}\frac{1}{\sigma_j \sqrt{2\pi}} \: e^{- \frac{\left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2}{2\sigma_j^2} }= \frac{1}{W_B} 
								\item This just says the pdf has to equal $\beta$ divided by the willingness to pay

@@

					\item How do we deal with this r.v. with continuous support when the range of ideal points is posited to be finite ($[-\frac{1}{2},\frac{1}{2}]$)?

				\end{itemize}
		\end{itemize}	
	\item Vote buyer A
		\begin{itemize}
			\item Whatever we decide for vote buyer B will be the same for vote buyer A
		\end{itemize}
\end{enumerate}
